\documentclass[conference]{IEEEtran}
\usepackage{enumerate}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage{bbm}
\usepackage[bb=boondox]{mathalfa}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{tikz}
\usepackage{bbold}
\usetikzlibrary{matrix}
\usepackage{subcaption}
\usepackage{url}

\begin{document}
\title{
''Drive-by-Wire"
\\[0.5cm]
\large{Studies on Mechatronics FS 2017}
}

\author{\IEEEauthorblockN{Noah Isaak}
\IEEEauthorblockA{student number: \\ 13-929-476}
\and

\IEEEauthorblockN{Richard von Moos}
\IEEEauthorblockA{student number: \\ 10-935-740}
}

\maketitle

%% Definitions by LF
\setlength\parindent{0pt}
\newcommand{\spn}[1]{\textsc{Span} \left\{ #1 \right\}}
\newcommand{\dimension}[1]{\textsc{dim} \left\{ #1 \right\}}
\newcommand{\real}[1]{\textsc{Re} \left( #1 \right)}
\newcommand{\imag}[1]{\textsc{Im} \left( #1 \right)}
\newcommand{\DET}[1]{\textsc{Det} \left[ #1 \right]}
\newcommand*\rfrac[2]{{}^{#1}\!/_{#2}}


\thispagestyle{plain}
\pagestyle{plain}

%\begin{abstract}
%The abstract goes here.
%\end{abstract}


\section{Introduction}

%Motivation
The decision to write a paper on the state of the art of drive-by-wire systems came natural, as we were designing a drive-by-wire system ourselves for our bachelor thesis. With the rise in popularity of electric cars, manufacturers and research groups see new opportunities in overhauling the previous methods of controlling a car. This rise in interest led to many approaches and solutions. The idea of this paper is not to gain new insights, but to provide the reader with a basic understanding of this topic. The content of this paper is mostly based on the findings of the state of the art technology.

%List papers
The paper is structured as follows. An overview of a drive-by-wire system is given in section II. In Section III we show the different ways how the vehicle dynamics were modelled and implemented in papers [1]-[?]

Section IV discusses common control algorithms mentioned in the various papers we read, namely sliding mode control, fuzzy control and h-infinity control. 

In the early years of the drive-by-wire technology, an implementation seemed far fetched.

\section{Drive by Wire}

\subsection{Steer by Wire}
\subsection{Throttle by Wire}
\subsection{Brake by Wire}
\section{Vehicle Dynamics, Vehicle Model}

\section{Control Algorithms}
\subsection{Sliding Mode Control}
\subsection{Fuzzy Control}
\subsection{H-Infinity Control}


\section{Results and Discussion}




\section{Conclusion}

De richi stenkt 

\begin{thebibliography}{1}
\bibitem{Weidong}
Weidong Xiang, Paul C. Richardson, Chenming Zhao, Syed Mohammad, 
\emph{Automobile Brake-by-Wire Control System Design and Analysis}, 
NO.1, January 2008.
http://ieeexplore.ieee.org/document/4358463/

\bibitem{Worldcongress2008}
Yasushi Aoki, Kenji Suzuki, Hiroshi Nakano, Kohei Akamine, Takaomi Shirase, Kouji Sakai, 
\emph{Development of Hydraulic Servo Brake for Cooperative Control with Regenerative Brake}
http://papers.sae.org/2007-01-0868/

\bibitem{Lenkungshandbuch}
Peter Pfeffer, Manfred Harrer, \emph{Lenkungshandbuch: Lenksysteme, Lenkgefühl, Fahrdynamik von Kraftfahrzeugen} http://www.springer.com/de/book/9783658009762
\textbf{Abschnitt R, Steer-by-wire}

\bibitem{JSME}
Se-Wook Oh, Ho-Chol Chae, Seok-Chan Yun, Chang-Soo Han
\emph{The Design of a Controller for the Steer-by-Wire System}
\url{https://www.jstage.jst.go.jp/article/jsmec/47/3/47_3_896/_article/}

\bibitem{Zheng}
B. Zheng, S. Anwar
\emph{Yaw stability control of a steer-by-wire equipped vehicle via active front wheel steering}
http://www.sciencedirect.com/science/article/pii/S0957415809000804

\bibitem{Yamaguchi}
Yousuke Yamaguchi, Toshiyuki Murakami
\emph{Adaptive Control for Virtual Steering Characteristics on Electric Vehicle Using Steer-by-Wire System}
http://ieeexplore.ieee.org/abstract/document/4689398/

\bibitem{vandersande}
T. van der Sande, P. Zegelaar, I. Besselink, H. Nijmeijer
\emph{A robust control analysis for a steer-by-wire vehicle with uncertainty on the tyre forces}
http://www.tandfonline.com/doi/full/10.1080/00423114.2016.1197407

\bibitem{Song}
Pan Song, Masayoshi Tomizuka, Changfu Zong
\emph{A novel integrated chassis controller for full drive-by-wire vehicles}
http://www.tandfonline.com/doi/abs/10.1080/00423114.2014.991331



\end{thebibliography}

\end{document}
